Conversations in Time: Interactive Visualization to Explore Structured Temporal Data

### 2021-07-28 rjdistill_version/tsibbletalk.Rmd
new r chunk for external scripts

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold',
  cache = TRUE, cache.path = 'cache/',
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
opts_knit$set(root.dir = here::here())
read_chunk("scripts/demo.R")
read_chunk("scripts/tourism.R")
read_chunk("scripts/pedestrian.R")
```

```{r, load-pkgs}
```

>>>>

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold',
  cache = TRUE, cache.path = 'cache/',
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
opts_knit$set(root.dir = here::here())
```

```{r external}
read_chunk("scripts/demo.R")
read_chunk("scripts/tourism.R")
read_chunk("scripts/pedestrian.R")
```

```{r load-pkgs}
```
